SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-28 docs/questioning.tex
minor changes

A malicious user can initiate the attack through two different routes.
The attacker may use the browser of an innocent user as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could craft a malicious script into a {\sc url}
and then trick an end user to click on it via social engineering (i.e., phishing).
({\sc step}: {\sc csrf} 1 \text{\textbar} {\sc p-xss}' 1 \text{\textbar} {\sc n-xss}' 1).
Alternatively, the attacker may be able to inject
directly the malicious code in the application. For example, consider
a web application that accepts and redisplays user input
without appropriate validation. An attacker could
upload data containing a specially crafted script (for example, in a
blog comment) to steal the cookies of the visiting users or embed
malicious {\sc sql} code to retrieve all the password entries from a
database ({\sc step}: {\sc dsl} 1 \text{\textbar}
{\sc p-xss} 1 \text{\textbar} {\sc n-xss} 1).
Note that an {\sc xss} attack can start from both routes.

@@

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.55]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model demonstrating web
application attacks based on executable source
code injection vulnerabilities. For every arrow there is a
corresponding tuple that includes the step number for
every attack. {\sc p-xss} stands for a persistent {\sc xss}
attack and {\sc n-xss} stands for a non persistent {\sc xss}
attack. Note that {\sc xss} attacks can also involve
{\it phishing}. Every {\it locus} indicates a step where mechanisms
detect attacks. For every locus we provide the corresponding
references: ({\sc draft}).}
\end{figure*}

@@

\section{Approaches}
\label{sec:defs}

Figure~\ref{fig:defenses} presents a taxonomy of the
approaches that protect web applications against attacks based on
code injection vulnerabilities.
We can identify two main approaches, namely:
{\it design-based} and {\it behavior-based}.
The former involves mechanisms that make applications
immune to different attack vectors by design~\cite{JL75,L81}.
The latter incorporates a variety of methods and
schemes that inspect the behavior of applications
and detect attacks based on specific criteria~\cite{D76,A00}.
Both categories involve more than one subcategories.
For every subcategory we provide elements regarding
every dimension described in Section~\ref{sec:dimensions}.

>>>>

A malicious user can initiate the attack through two different routes.
The attacker may use the browser of an innocent user as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could craft a malicious script into a {\sc url}
and then trick an end user to click on it via social engineering (i.e., phishing).
({\sc step}: {\sc p-xss}' 1 \text{\textbar} {\sc n-xss}' 1 \text{\textbar} {\sc csrf} 1).
Alternatively, the attacker may be able to inject
directly the malicious code in the application. For example, consider
a web application that accepts and redisplays user input
without appropriate validation. An attacker could
upload data containing a specially crafted script (for example, in a
blog comment) to steal the cookies of the visiting users or embed
malicious {\sc sql} code to retrieve all the password entries from a
database ({\sc step}: {\sc dsl} 1 \text{\textbar}
{\sc p-xss} 1 \text{\textbar} {\sc n-xss} 1).
Note that an {\sc xss} attack can start from both routes.

@@

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.55]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model demonstrating web
application attacks based on executable source
code injection vulnerabilities. For every arrow there is a
corresponding tuple that includes the step number for
every attack. Note that {\sc xss} attacks can also involve
{\it phishing}. Every {\it locus} indicates a step where mechanisms
detect attacks. For every locus we provide the corresponding
references: ({\sc draft}).}
\end{figure*}

@@

\section{Defenses}
\label{sec:defs}

Figure~\ref{fig:defenses} presents a taxonomy of the
defenses that protect web applications against attacks based on
code injection vulnerabilities.
We can identify two main approaches, namely:
{\it design-based} and {\it behavior-based}.
The former involves mechanisms that make applications
immune to different attack vectors by design~\cite{JL75,L81}.
The latter incorporates a variety of methods and
schemes that inspect the behavior of applications
and detect attacks based on specific criteria~\cite{D76,A00}.
Both categories involve more than one subcategories.
For every subcategory we provide elements regarding
every dimension described in Section~\ref{sec:dimensions}.
